### 2025-09-29 src/articles/article6.qmd
fix article linking

# Finances

## General Rules

@@

## Budget

1. The Treasurer will present a preliminary budget to the Budget Committee (Article V, Section G, Item 2c) no later than six weeks before the beginning of the Fall Semester.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
1. Budget Committee
   a. The Budget Committee (Article V, Section G, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
   a. Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).

## Financial Obligations of Members

@@

## Deferments

@@

## Payment Schedule and Penalties

@@

## Financial Privacy Section

@@

## Reimbursements

>>>>

# Finances {#sec-art-NV6E374B}

## General Rules {#sec-art-SKY8T9UM}

@@

## Budget {#sec-art-GD7C1K2U}

1. The Treasurer will present a preliminary budget to the Budget Committee (@sec-art-VI2T9PVL, Item 2c) no later than six weeks before the beginning of the Fall Semester.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
1. Budget Committee
   a. The Budget Committee (@sec-art-VI2T9PVL, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
   a. Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).

## Financial Obligations of Members {#sec-art-VDN0D2P4}

@@

## Deferments {#sec-art-OUD16M61}

@@

## Payment Schedule and Penalties {#sec-art-1ATKL12C}

@@

## Financial Privacy Section {#sec-art-KK0JMIWX}

@@

## Reimbursements {#sec-art-FCOCY19N}

### 2025-09-29 src/articles/article8.qmd
fix article linking

# Awards

## Award Election Procedure

@@

## Specified Awards

@@

1. Dream Girl Award:
   a. Will be bestowed upon the woman associated with Beta Nu Chapter who has done the most for the presently active chapter.
   a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
   a. Voting will be done by {{< var glossary.ballot >}} in direct exception to Article VIII, Section A, Item 1b.

1. Certificate of Appreciation:
   a. May be presented to any person who has demonstrated service of extraordinary care and effort to the chapter.\
   a. Will consist of a certificate of appropriate construction and suitable wording which describes the service for which the certificate is being presented.
   a. Any brother eligible to vote may, at any chapter meeting, nominate any person.
   a. Discussion will be allowed for this award in direct exception to Article VIII, Section A, Item 1c.
   a. A nominee must receive a {{< var glossary.supermajority >}} vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
   a. The chapter may give out any number of this award.

1. The chapter may give out any other awards subject to the procedures defined in Article VIII, Section A.

>>>>

# Awards {#sec-art-KAF5NVBG}

## Award Election Procedure {#sec-art-WWI418WD}

@@

## Specified Awards {#sec-art-GZYYZN72}

@@

1. Dream Girl Award:
   a. Will be bestowed upon the woman associated with Beta Nu Chapter who has done the most for the presently active chapter.
   a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
   a. Voting will be done by {{< var glossary.ballot >}} in direct exception to @sec-art-WWI418WD, Item 1b.

1. Certificate of Appreciation:
   a. May be presented to any person who has demonstrated service of extraordinary care and effort to the chapter.\
   a. Will consist of a certificate of appropriate construction and suitable wording which describes the service for which the certificate is being presented.
   a. Any brother eligible to vote may, at any chapter meeting, nominate any person.
   a. Discussion will be allowed for this award in direct exception to @sec-art-WWI418WD, Item 1c.
   a. A nominee must receive a {{< var glossary.supermajority >}} vote to receive this award in direct exception to @sec-art-WWI418WD, Item 1b.
   a. The chapter may give out any number of this award.

1. The chapter may give out any other awards subject to the procedures defined in @sec-art-WWI418WD.
